%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[12pt]{article}

% Page layout
\setlength\topmargin{0cm}
\setlength\textwidth{16.5cm}
\setlength\oddsidemargin{0cm}
\setlength\evensidemargin{0cm}
\setlength\headheight{0cm}
\setlength\textheight{21cm}

% Date formatting
\usepackage{datetime}
\newdateformat{sigdate}{\ordinaldate{\THEDAY} day of \monthname[\THEMONTH], \THEYEAR}

% Line spacing
\usepackage{setspace}
\doublespacing

% New Commands
%
% My client
\newcommand{\client}{ABC Corporate Enterprises, Inc. }
\newcommand{\csn}{ABCCE }


% Will Robertson's fontspec.sty can be used to simplify font choices.
% To experiment, open /Applications/Font Book to examine the fonts provided on Mac OS X,
% and change "Hoefler Text" to any of these choices.

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Hoefler Text}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans}
\setmonofont[Scale=MatchLowercase]{Andale Mono}

\begin{document}
\singlespacing

\begin{center}
UNITED STATES DISTRICT COURT\\
WESTERN DISTRICT OF NORTH CAROLINA\\
CHARLOTTE DIVISION\\
\end{center}

\doublespacing

\noindent Patent Troll, Inc.

\noindent \hspace{2cm}Plaintiff,

\noindent v.\ \hspace{9cm}Civil Action No.:  3:08CV0666-C

\noindent \client

\noindent \hspace{2cm}Defendant.\

\noindent \line(1,0){200}

\singlespacing
\begin{center}
Defendant ABC Corporate Enterprises, Inc.'s Answer to Plaintiff's Amended Complaint
\end{center}

\doublespacing

Defendant \client (``\csn''), by and through its undersigned attorneys, files this answer to the Plaintiff's Complaint and states as follows:

\begin{enumerate}
\item Denied.
\item Denied.
\item Denied.
\item Admitted.
\item \csn is without sufficient information to form a belief as to the truth of the allegations contained in paragraph 5, and therefore they are denied.
\item Denied.
\item \csn is without sufficient information to form a belief as to the truth of the allegations contained in paragraph 7, and therefore they are denied.
\item \csn is without sufficient information to form a belief as to the truth of the allegations contained in paragraph 8, and therefore they are denied.
\item Denied.
\item Denied.
\item \csn is without sufficient information to form a belief as to the truth of the allegations contained in paragraph 11, and therefore they are denied.
\item Denied.
\item Denied.
\item Denied.
\item \csn reincorporates its answers from paragraphs 1--14 above.
\item Denied.
\item \csn without sufficient information to form a belief as to the truth of the allegations contained in paragraph 16, and therefore they are denied.
\end{enumerate}

Wherefore \csn prays this Court to dismiss the Plaintiff's Amended Complaint in its entirety and award to \csn all costs, fees, and other such relief as this Court deems just.\newpage

Respectfully submitted this \sigdate\today.

\vspace{1cm}

\singlespacing
\hspace{7cm}\line(1,0){150}

\hspace{7cm}Bob Smith

\hspace{7cm}NC No. 12345

\hspace{7cm}Attorneys for \client

\hspace{7cm}Example Law Firm, PLLC

\hspace{7cm}720 Michigan Avenue

\hspace{7cm}Chicago, IL 55555

\hspace{7cm}Telephone: 312

\hspace{7cm}E-mail: bob.smith@lawfirm.com

\end{document}  